---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit this file. -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# labtoolbox

<!-- badges: start -->
<!-- badges: end -->

Alyssa [Huberts](https://github.com/alyssa-huberts), Ryan T. [Moore](https://github.com/rtm-dc)

The `{labtoolbox}` package provides functions to simplify and automate common data analysis and presentation tasks for The Lab @ DC.


## Installation

You can install the development version of `{labtoolbox}` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("thelabdc/labtoolbox")
```

You may need to manually install package `{sysfonts}` with
`install.packages("sysfonts")`.

## Example

```{r example, fig.height=3}
library(labtoolbox)

# Make treatment effect barplot with sample data:
make_ci_barplot()
```

## Compilation

In order to include R chunks, we use `README.Rmd` instead of `README.md`. We render `README.Rmd` regularly with `devtools::build_readme()`.
