---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# labtoolbox

<!-- badges: start -->
<!-- badges: end -->

Alyssa [Huberts](https://github.com/alyssa-huberts), Ryan T. [Moore](https://github.com/rtm-dc)

The `{labtoolbox}` package provides functions to simplify and automate common data analysis and presentation tasks for The Lab @ DC.


## Installation

You can install the development version of labtoolbox from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("thelabdc/labtoolbox")
```

## Example

This is where we will keep examples of the package's functions. 

```{r example}
library(labtoolbox)
## basic example code
```

(We use `README.Rmd` instead of just `README.md` to include R chunks. We still need to render `README.Rmd` regularly with `devtools::build_readme()`.)
